### 2020-06-22 Strings2020/strings6/strings6.tex
Complete strings6

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
% !TeX TS-program = xelatex
%%% LuaLaTeX is required for `tikz-feynman`

@@

\newcommand{\hwNumber}{6 [WIP]}

@@

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

@@

@@

	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions. In fact, closure of OPE implies that the $(\NS+, \NS+)$ sector must exist. In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e. it is possible (but not required) to have a $(\NS-, \NS-)$ sector.

	The full possiblities can then be generated by enumerating all possible (R, R) sectors (there are $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
	\begin{equation}
		\exp i\pi \pqty{
				  F_1 \alpha_2
				- F_2 \alpha_1
				- \tilde{F}_1 \tilde{\alpha}_2
				+ \tilde{F}_2 \tilde{\alpha}_1
			}
		= 1
	\end{equation}
	If $O_1 \in (\,\NS+, \NS+)$, then we have $\alpha_1 = \tilde{\alpha}_1 = 0 = F_1 = \tilde{F}_1$, hence the above factor is always trivial; for $O_1 \in (\R,\R)$, however, $\alpha_1 = \tilde{\alpha}_1 = 1$, which yields a non-trivial constraint for the second operator: $
		F_2 - \tilde{F}_2
		= F_1 \alpha_2 - \tilde{F}_1 \tilde{\alpha}_2
		= \alpha_2 \pqty\big{F_1 - \tilde{F}_1}
		\ (\mop{mod} 2)
	$, assuming $\alpha_2 = \tilde{\alpha}_2$. With $\alpha_2 = 0$ this gives $F_2 = \tilde{F}_2$, and with $\alpha_2 = 1$ this gives $
		F_2 - \tilde{F}_2
		= F_1 - \tilde{F}_1
	$; this means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
	\begin{gather}
		\mrm{0A}\colon\ %
			(\NS+,\NS+),\ %
			(\NS−,\NS−),\ %
			(\R+,\R-),\ %
			(\R−,\R+), \\
		\mrm{0B}\colon\ %
			(\NS+,\NS+),\ %
			(\NS−,\NS−),\ %
			(\R+,\R+),\ %
			(\R−,\R−), \\
		\text{And additionally, $(\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
		\label{eq:type0_deviant}
	\end{gather}

	If there are two (R, R) sectors, then there must be an acompanying $(\NS−,\NS−)$ sector due to the closure of OPE. It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).

@@

	\item \textbf{Fiberwise T-Duality and the Dilaton}
	\begin{enumerate}
	\item For a bosonic string moving in a general background of massless fields in $D = d + 1 = 26$, its worldsheet action is given by:
	\begin{equation}
		S = \frac{1}{4\pi\alpha'}
			\int \dd[2]{\sigma} \sqrt{g}\,
			\Bqty\Big{
				\pqty{
					g^{ab} G_{MN}(X)
					+ i\epsilon^{ab} B_{MN}(X)
				}\,
				\pdd{a} X^M
				\pdd{b} X^N
				+ \alpha'\mcal{R}\,\Phi(X)
			}
	\end{equation}
	Where $\Phi$ is the worldsheet Ricci scalar. The $X^{25}$ direction is to be compactified, and the background fields $G_{MN}, B_{MN}$ and $\Phi$ depends only on $X^\mu,\,\mu = 0,1,\cdots,(d-1) = 24$.

	$G_{MN}$ can be further split into $G_{\mu\nu},G_{\mu d}$ and $G_{dd}$ with $d = 25$, in a way similar to \eqref{eq:metric_decomp}, but here we are using a simpler convention, with $G^D_{\mu\nu} = G_{\mu\nu}$ instead of \eqref{eq:sub_metric_convention}. Similar goes for $B_{MN}$, with $B_{\mu\nu},B_{\mu d}$, and $B_{dd} = 0$, due to anti-symmetricity.

	\item After replacing $\pdd{a} X^d\mapsto \pdd{a} X^d + A_a$ where $A_a$ is an auxilary abelian gauge field on the worldsheet, the $X^d$ related parts in the Lagrangian become:
	\begin{equation}
	\small
	\begin{aligned}
		\mcal{L}_d[X^d,A_a]
		&= \frac{\sqrt{g}}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty{
					g^{ab} G_{\mu d}
					+ i\epsilon^{ab} B_{\mu d}
				}
					\,(\pdd{a} X^d + A_a)\,
					\pdd{b} X^\mu
				+ g^{ab} G_{dd}
					\,(\pdd{a} X^d + A_a)\,
					\,(\pdd{b} X^d + A_b)
			} \\
	\end{aligned}
	\end{equation}

@@

	In fact, we would like $A_a$ to be ``pure gauge'', capturing only the $X^d$ translational symmetry and nothing more; this can be achieved by adding yet another auxilary field $\phi(\sigma)$ and an extra term:
	\begin{equation}
		\mcal{L}_d
		\longmapsto \mcal{L}_d
			+ i\epsilon^{ab} F_{ab}\,\phi,
	\quad
		F_{ab}
		= \pdd{a} A_b - \pdd{b} A_a,
	\quad
		\int \DD{\phi}\,
			e^{-i\epsilon^{ab} F_{ab}\,\phi}
		\sim \delta\bqty{
				\epsilon^{ab} F_{ab}
			}
	\end{equation}
	Which forces $F_{12} \equiv 0$ in the remaining path integral. Note that the only non-zero independent component of $F_{ab}$ in 2D is $F_{12}$, therefore $F_{12} \equiv 0$ implies that $F_{ab} \equiv 0$, or $
		F = \dd{A} = 0
	$. On the plane, this implies that $A = \dd{\lambda}$, i.e.\ it is indeed pure gauge\footnote{
		However, if there are punctures on the worldsheet, then there is non-trivial cohomology, and $A$ need not be $\dd{\lambda}$. I have not yet understood how this would affect our result; this problem is also acknowledged in \textit{Blumenhagen et al}, Chapter 14, yet it seems to simply ignore such issue. 
	}.

@@

	\item Following our discussions in (b), we see that:
	\begin{equation}
		\pdd{a} X^d + A_a
		= 0 + A_a - \pdd{a} \lambda,\quad
		\lambda = -\pdd{a} X^d,
%	\\
%		\int \DD{X^d}\,
%			e^{-S'[X,\phi,A]}
%		= \int \DD{\lambda}\,
%			e^{-S'[X^d\equiv 0,\phi,A_\lambda]},\quad
%		A_\lambda = A - \dd{\lambda},
	\end{equation}
%	i.e.\ integrating over $X^d$ is equivalent to integrating over all the gauge configurations of $A$, labeled by $\lambda$, but with $X^d \equiv 0$. 
	Before completing the path integral, we perform a gauge transformation $
		A_a \mapsto A_a - \pdd{a} \lambda
	$, with $\lambda =  -X^d$. Assuming that there is no anomaly, we can ignore the functional Jacobian of the transformation, and the path integral shall be gauge invariant; in this case, the $\pdd{a} X^d$ term is canceled precisely by the gauge transformation, which is equivalent to setting $X^d = 0$ in the action:
	\begin{equation}
		S''\bqty{
				X^\mu,\phi,A
			}
		= S'\bqty{
				X^\mu,X^d = 0,\phi,A
			}
	\end{equation}

@@

	\legacyReference

	\begin{enumerate}
	\item Mode expansion of $X$ CFT is\footnote{
		Again we follow the convention of \textit{Polchinski}. 
	}:
	\begin{gather}
		\pd X(z) =
			-i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{\alpha_m}{z^{m+1}},\quad
		\pdbar X(\bar{z}) =
			-i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{\tilde{\alpha}_m}{\bar{z}^{m+1}},\\
		X = x
			- i\,\sqrt{\frac{\alpha'}{2}}
			\,\pqty\big{
				\alpha_0 \ln z
				+ \tilde{\alpha}_0 \ln \bar{z}
			}
			+ i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m \ne 0}
				\frac{1}{m}
				\pqty{
					\frac{\alpha_m}{z^m}
					+ \frac{\tilde{\alpha}_m}{\bar{z}^m}
				},
	\end{gather}
	Momentum $p$ is the charge for \textit{spacetime} translation; we have:
	\begin{gather}
		X\mapsto X + \mrm{const},\quad
		j_a = \frac{i}{\alpha'}\,\pdd{a} X,
	\\
		p = \frac{1}{2\pi i} \oint_C \pqty{
				\dd{z} j - \dd{\bar{z}} \tilde{j}\,
			}
		= \frac{1}{\alpha'} \sqrt{\frac{\alpha'}{2}}\,
			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
		= \sqrt{\frac{1}{2\alpha'}}\,
			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
	\end{gather}

	Additionally, for compact free boson, $X$ is only defined modulo $2\pi R$; therefore, states after $X + 2\pi R$ translation should be identical to the original states, i.e.
	\begin{equation}
		e^{ip\,(2\pi R)} = \idty,\quad
		p = \frac{n}{R},\quad n\in\mbb{Z}
	\end{equation}
	This, in fact, holds for any field theory\footnote{
		Reference: discussions in \textit{Polchinski}, Chapter 8. 
	} defined for $X\in S^1$, including the ordinary quantum mechanics (a classical field theory) on $S^1$.

	On the other hand, there are additional constraints in string theory: for the state of a \textit{single} closed string, there is a discrete translational symmetry on the \textit{worldsheet}:
	\begin{equation}
		X(\sigma^1 + 2\pi) \cong X(\sigma^1),\quad
		X(\sigma^1 + 2\pi) = X(\sigma^1) + 2\pi Rw,\quad
		w \in\mbb{Z}
	\end{equation}
	With some definite winding number $w$. In $(z,\bar{z})$ coordinates, we have:
	\begin{gather}
		2\pi Rw
		= X\pqty{
				z\,e^{2\pi i},\zbar\,e^{-2\pi i}\,
			} - X(z,\zbar)
		= -i\sqrt{\frac{\alpha'}{2}}\,
			2\pi i\,\pqty\big{
				\alpha_0 - \tilde{\alpha}_0
			}
		= 2\pi\sqrt{\frac{\alpha'}{2}}\,
			\pqty\big{
				\alpha_0 - \tilde{\alpha}_0
			},
	\\
		p = \frac{p_L + p_R}{2},\quad
		p_L = \sqrt{\frac{2}{\alpha'}}\,\alpha_0,\quad
		p_R = \sqrt{\frac{2}{\alpha'}}\,\tilde{\alpha}_0,
	\\[1ex]
		p_{L,R} = \frac{n}{R} \pm \frac{wR}{\alpha'}\,,
	\\[1ex]
		X = x
			- i\,\frac{\alpha'}{2}\,
			\pqty\big{
				p_L \ln z
				+ p_R \ln \bar{z}
			}
			+ i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m \ne 0}
				\frac{1}{m}
				\pqty{
					\frac{\alpha_m}{z^m}
					+ \frac{\tilde{\alpha}_m}{\bar{z}^m}
				},
	\end{gather}

	For the oscillator expressions for $L_0$, recall that:
	\begin{gather}
		T(z)
		= - \frac{1}{\alpha'}\,
			\normorder{\pd X\,\pd X}
		= \sum_m \frac{L_m}{z^{m+2}},
	\\
		L_{m\ne 0}
		= \frac{1}{2}
			\sum_l \alpha_{m-l} \alpha_l,\quad
		L_0 = \frac{1}{2}\,\normorder{
			\sum_l \alpha_{-l} \alpha_l
		}
		\sim \frac{\alpha'p_L^2}{4}
			+ \sum_{l > 0} \alpha_{-l} \alpha_l,
	\end{gather}
	The $L_0$ expression may be off by some normal ordering constant; this ambiguity can be resolved by considering:
	\begin{equation}
		2L_0 \ket{0,0;n = w = 0}
		= \pqty{
				L_1 L_{-1} - L_{-1} L_1
			} \ket{0,0;p_L = p_R = 0}
		= 0 - 0 = 0
	\end{equation}
	Therefore the normal ordering constant is, in fact, trivial, and we have:
	\begin{equation}
		L_0 = \frac{\alpha'p_L^2}{4}
			+ \sum_{l > 0}
				\alpha_{-l} \alpha_l,\quad
		\tilde{L}_0 = \frac{\alpha'p_R^2}{4}
			+ \sum_{l > 0}
				\tilde{\alpha}_{-l} \tilde{\alpha}_l,
	\end{equation}

>>>>

% !TeX document-id = {39d24ce0-844d-44a8-943b-2a9698211621}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
% !TeX TS-program = xelatex
%%% LuaLaTeX is required for `tikz-feynman`

@@

\newcommand{\hwNumber}{6}

@@

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}

@@

\addbibresource{strings6.bib}

@@

	If we include only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions. In fact, closure of OPE implies that the $(\NS+, \NS+)$ sector must exist. In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e. it is possible (but not required) to have a $(\NS-, \NS-)$ sector.

	All possibilities can then be generated by enumerating all possible (R, R) sectors (there are $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
	\begin{equation}
		\exp i\pi \pqty{
				  F_1 \alpha_2
				- F_2 \alpha_1
				- \tilde{F}_1 \tilde{\alpha}_2
				+ \tilde{F}_2 \tilde{\alpha}_1
			}
		= 1
	\end{equation}
	If $O_1 \in (\,\NS+, \NS+)$, then we have $\alpha_1 = \tilde{\alpha}_1 = 0 = F_1 = \tilde{F}_1$, hence the above factor is always trivial; for $O_1 \in (\R,\R)$, however, $\alpha_1 = \tilde{\alpha}_1 = 1$, which yields a non-trivial constraint for the second operator: $
		F_2 - \tilde{F}_2
		= F_1 \alpha_2 - \tilde{F}_1 \tilde{\alpha}_2
		= \alpha_2 \pqty\big{F_1 - \tilde{F}_1}
		\ (\mop{mod} 2)
	$, assuming $\alpha_2 = \tilde{\alpha}_2$. With $\alpha_2 = 0$ this gives $F_2 = \tilde{F}_2$, and with $\alpha_2 = 1$ this gives $
		F_2 - \tilde{F}_2
		= F_1 - \tilde{F}_1
	$; this means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
	\begin{gather}
		\mrm{0A}\colon\ %
			(\NS+,\NS+),\ %
			(\NS−,\NS−),\ %
			(\R+,\R-),\ %
			(\R−,\R+), \\
		\mrm{0B}\colon\ %
			(\NS+,\NS+),\ %
			(\NS−,\NS−),\ %
			(\R+,\R+),\ %
			(\R−,\R−), \\
		\text{And additionally, $(\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
		\label{eq:type0_deviant}
	\end{gather}

	If there are two (R, R) sectors, then there must be an accompanying $(\NS−,\NS−)$ sector due to the closure of OPE. It is straightforward to check that these possibilities are all valid under the above constraints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).

@@

	\item \textbf{Fiberwise T-Duality and the Dilaton}
	\begin{enumerate}
	\item For a bosonic string moving in a general background of massless fields in $D = d + 1 = 26$, its worldsheet action is given by:
	\begin{equation}
		S = \frac{1}{4\pi\alpha'}
			\int \dd[2]{\sigma} \sqrt{g}\,
			\Bqty\Big{
				\pqty{
					g^{ab} G_{MN}(X)
					+ i\epsilon^{ab} B_{MN}(X)
				}\,
				\pdd{a} X^M
				\pdd{b} X^N
				+ \alpha'\mcal{R}\,\Phi(X)
			}
	\end{equation}
	Where $\Phi$ is the worldsheet Ricci scalar. The $X^d \equiv X^{25}$ direction is to be compactified, and the background fields $G_{MN}, B_{MN}$ and $\Phi$ depends only on $X^\mu,\,\mu = 0,1,\cdots,(d-1) = 24$.

	$G_{MN}$ can be further split into $G_{\mu\nu},G_{\mu d}$ and $G_{dd}$ with $d = 25$, in a way similar to \eqref{eq:metric_decomp}, but here we are using a simpler convention, with $G^D_{\mu\nu} = G_{\mu\nu}$ instead of \eqref{eq:sub_metric_convention}. Similar goes for $B_{MN}$, with $B_{\mu\nu},B_{\mu d}$, and $B_{dd} = 0$, due to anti-symmetry.

	\item After replacing $\pdd{a} X^d\mapsto \pdd{a} X^d + A_a$ where $A_a$ is an auxiliary abelian gauge field on the worldsheet, the $X^d$ related parts in the Lagrangian become:
	\begin{equation}
	\small
	\begin{aligned}
		\mcal{L}_d[X^d,A_a]
		&= \frac{\sqrt{g}}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty{
					g^{ab} G_{\mu d}
					+ i\epsilon^{ab} B_{\mu d}
				}
					\,(\pdd{a} X^d + A_a)\,
					\pdd{b} X^\mu
				+ g^{ab} G_{dd}
					\,(\pdd{a} X^d + A_a)\,
					\,(\pdd{b} X^d + A_b)
			}
	\end{aligned}
	\end{equation}

@@

	In fact, we would like $A_a$ to be ``pure gauge'', capturing only the $X^d$ translational symmetry and nothing more; this can be achieved by adding yet another auxiliary field $\phi(\sigma)$ and an extra term:
	\begin{equation}
		\mcal{L}_d
		\longmapsto \mcal{L}_d
			+ i\epsilon^{ab} F_{ab}\,\phi,
	\quad
		F_{ab}
		= \pdd{a} A_b - \pdd{b} A_a,
	\quad
		\int \DD{\phi}\,
			e^{-i\epsilon^{ab} F_{ab}\,\phi}
		\sim \delta\bqty{
				\epsilon^{ab} F_{ab}
			}
	\end{equation}
	Which forces $F_{12} \equiv 0$ in the remaining path integral. Note that the only non-zero independent component of $F_{ab}$ in 2D is $F_{12}$, therefore $F_{12} \equiv 0$ implies that $F_{ab} \equiv 0$, or $
		F = \dd{A} = 0
	$. On the plane, this implies that $A = \dd{\lambda}$, i.e.\ it is indeed pure gauge\footnote{
		However, if there are punctures on the worldsheet, then there is non-trivial cohomology, and $A$ need not be $\dd{\lambda}$. 
		Instead, the gauge field can have non-trivial holonomy around the cycles of the worldsheet. One can show that these holonomies are gauge trivial if $\phi$ has periodicity $2\pi$. In this case, the partition function is again equivalent to the original one. Reference: \textit{Tong}, String Theory; see also \arxiv{0812.4408}. 
	}.

@@

	\item Following our discussions in (b), we see that:
	\begin{equation}
		\pdd{a} X^d + A_a
		= 0 + A_a - \pdd{a} \lambda,\quad
		\lambda = -\pdd{a} X^d,
%	\\
%		\int \DD{X^d}\,
%			e^{-S'[X,\phi,A]}
%		= \int \DD{\lambda}\,
%			e^{-S'[X^d\equiv 0,\phi,A_\lambda]},\quad
%		A_\lambda = A - \dd{\lambda},
	\end{equation}
%	i.e.\ integrating over $X^d$ is equivalent to integrating over all the gauge configurations of $A$, labeled by $\lambda$, but with $X^d \equiv 0$. 
	Before completing the path integral, we perform a gauge transformation $
		A_a \mapsto A_a - \pdd{a} \lambda
	$, with $\lambda =  -X^d$. Assuming that there is no anomaly, we can ignore the functional Jacobian of the transformation, and the path integral shall be gauge invariant; in this case, the $\pdd{a} X^d$ term is canceled precisely by the gauge transformation, which is equivalent to setting $X^d = 0$ in the action:
	\begin{equation}
		S\bqty{
				X^\mu,\phi,A
			}
		= S'\bqty{
				X^\mu,X^d = 0,\phi,A
			}
	\end{equation}

	Furthermore, the $A_a$ related parts in the Lagrangian is now nice and quadratic:
	\begin{equation}
%	\small
	\begin{aligned}
		\mcal{L}_A
		&= \frac{\sqrt{g}}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty{
					g^{ab} G_{\mu d}
					+ i\epsilon^{ab} B_{\mu d}
				}\,A_a\,\pdd{b} X^\mu
				+ g^{ab} G_{dd}\, A_a A_b
				+ i\epsilon^{ab} F_{ab}\,\phi
			} \\
		&= \frac{\sqrt{g}}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty{
					g^{ab} G_{\mu d}
					- i\epsilon^{ab} B_{\mu d}
				}\,\pdd{a} X^\mu A_b
				+ g^{ab} G_{dd}\, A_a A_b
				+ 2i\epsilon^{ab} \phi\, \pdd{a} A_b
			} \\
		&\sim \frac{1}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty{
					\delta^{ab} G_{\mu d}
					- i\epsilon^{ab} B_{\mu d}
				}\,\pdd{a} X^\mu A_b
				+ \delta^{ab} G_{dd}\, A_a A_b
				- 2i\epsilon^{ab}
					\,\pdd{a}\phi\, A_b
			} \\
		&= \frac{1}{4\pi\alpha'}
			\Bqty\Big{
				2\,\pqty\Big{
					\pqty{
						\delta^{ab} G_{\mu d}
						- i\epsilon^{ab} B_{\mu d}
					}\,\pdd{a} X^\mu
					- i\epsilon^{ab} \,\pdd{a}\phi
				} A_b
				+ \delta^{ab} G_{dd}\, A_a A_b
			}
	\end{aligned}
	\end{equation}
	Here we've fixed the conformal gauge $g_{ab} = \delta_{ab}$ and integrated by parts, so that $
		\phi\, \pdd{a} A_b
		\mapsto -\pdd{a}\phi\, A_b
	$.

	It is convenient to define\footnote{
		Reference: \textit{Blumenhagen et al}, Basic Concepts of String Theory, Chapter 14. 
	}:
	\begin{equation}
	\begin{aligned}
		J^b
		&= \frac{1}{G_{dd}} \pqty\Big{
				\pqty{
					\delta^{ab} G_{\mu d}
					- i\epsilon^{ab} B_{\mu d}
				}\,\pdd{a} X^\mu
				- i\epsilon^{ab} \,\pdd{a}\phi
			}
	\end{aligned}
	\end{equation}
	The path integral over $A_a$ can then be completed as a Gaussian integral. Note that this time we integrate out $A_a$ first, leaving $\phi$ in place; therefore we do not impose any gauge fixing. We have:
	\begin{gather}
		\mcal{L}_A
		= \frac{G_{dd}}{4\pi\alpha'}
			\Bqty\Big{
				2J^b A_b
				+ \delta^{ab} A_a A_b
			}
		= \frac{G_{dd}}{4\pi\alpha'}
			\Bqty\Big{
				(A + J)^2
				- \delta^{ab} J_a J_b
			},
	\\[1ex]
		S = \int \dd[2]{\sigma} \pqty\big{
				\mcal{L}_A + \mcal{L}_0
			},
	\quad
		\int \DD{A_a}\,e^{-S}
		\sim \det \bqty{
				\frac{
					G_{dd}\pqty\big{X^\mu(\sigma)}
				}{2\pi\alpha'}
			}^{-\frac{1}{2}} e^{-\tilde{S}},
	\\[.5ex]
		\tilde{S} = \int \dd[2]{\sigma} \pqty{
				\mcal{L}_0
				- \frac{G_{dd}}{4\pi\alpha'}\,
					J^a J_a
			},
	\end{gather}

	If we identify $X^d \cong X^d + 2\pi$, then the radius of the $X^d$ circle is given by $R(X^\mu) = \sqrt{G_{dd}}$. When $R^2 \gg \alpha'$ or $R \gg \sqrt{\alpha'}$, the above path integral approaches the classical limit, and its main contribution comes from the classical saddle $A_a = -J_a$, which is included in the $e^{-\tilde{S}}$ factor. The functional determinant is sub-leading and can be ignored.

	Expand the action $\tilde{S}$ in terms of $(X^\mu,\phi)$, we find that:
	\begin{gather}
		\tilde{S} = \frac{1}{4\pi\alpha'}
			\int \dd[2]{\sigma}
			\Bqty\Big{
				\pqty{
					\delta^{ab} \tilde{G}_{MN}
					+ i\epsilon^{ab} \tilde{B}_{MN}
				}\,
				\pdd{a} \tilde{X}^M
				\pdd{b} \tilde{X}^N
%				+ \alpha'\mcal{R}\,\Phi(X)
			},\quad
		\tilde{X}
		= (\tilde{X}^\mu,\tilde{X}^d)
		= (X^\mu,\phi),
	\\
		\tilde{G}_{dd}
		= \frac{1}{G_{dd}},\quad
		\tilde{G}_{\mu d}
		= \frac{1}{G_{dd}} B_{\mu d},\quad
		\tilde{G}_{\mu\nu}
		= G_{\mu\nu}
			- \frac{1}{G_{dd}} \pqty\big{
				G_{\mu d} G_{\nu d}
				- B_{\mu d} B_{\nu d}
			},
	\\
		\tilde{B}_{\mu d}
		= \frac{1}{G_{dd}} G_{\mu d},\quad
		\tilde{B}_{\mu\nu}
		= B_{\mu\nu}
			- \frac{1}{G_{dd}} \pqty\big{
				G_{\mu d} B_{\nu d}
				- B_{\mu d} G_{\nu d}
			},
	\end{gather}
	i.e.\ we've found the T-dual theory with $\tilde{R}\propto \frac{1}{R}$. Rescale $\phi\mapsto \phi/\sqrt{\alpha'}$ and $G_{dd}\mapsto \alpha'G_{dd}$, we recover the usual result: $
		\tilde{R} = \frac{\alpha'}{R}
	$.

	\item Now we return to the determinant; roughly speaking, we have:
	\begin{equation}
		\det \bqty{
				\frac{
					G_{dd}\pqty\big{X^\mu(\sigma)}
				}{2\pi\alpha'}
			}^{-\frac{1}{2}}
		= \exp \pqty{
				- \frac{1}{2}
				\ln \det \bqty{\cdots}
			}
		\sim \exp \pqty{
				- \frac{1}{2}
				\tr \frac{\ln G_{dd}}{\alpha'}
			}
	\end{equation}
	Which appears to add a term $\sim - \frac{1}{2} \ln G_{dd}$ in the Lagrangian.

	However, the $\mquote{\det}$ and $\mquote{\tr}$ in the above equation are divergent and ill-defined, and would only make sense after some careful regularization\footnote{
		I would like to thank \textit{谷夏} for hints about this problem. 
	}, which was introduced by \textit{Buscher} \cite{Buscher:1987qj} and nicely reviewed by \textit{Alvarez et al} \cite{Alvarez:1994dn}. The regularized determinant along with the Jacobian adds the following contribution in the Lagrangian:
	\begin{equation}
		- \alpha'\mcal{R}\cdot \frac{1}{2}
			\ln \frac{G_{dd}}{\alpha'}
	\end{equation}
	Which is equivalent to a dilaton shift:
	\begin{equation}
		\tilde{\Phi}
		= \Phi - \frac{1}{2}
			\ln \frac{G_{dd}}{\alpha'}
	\end{equation}

	In the limit of constant size $R = \sqrt{G_{dd}}$, note that the string coupling $g_s \sim e^{\Phi_0}$, and we recover the usual result: $\tilde{g}_s = g_s \sqrt{\alpha'} / R$.

@@

	\item \textbf{Only One Coupling Constant in String Theory}\footnote{
		Reference: \arxiv{0812.4408}. 
	}
	\begin{enumerate}
	\item Consider the open string one-loop diagram, which is topologically a cylinder. To represent such geometry on the place, we start from the ``rectangular'' torus:
	\begin{equation}
		w \cong w + 2\pi \cong w + 2\pi\tau,\quad
		\tau = it
	\end{equation}
	And identify under an \textit{involution}, i.e.\ a reflection through the imaginary axis:
	\begin{equation}
		w' = -\bar{w},
	\quad\Longrightarrow\quad
		0 \le \Re w \le \pi
	\end{equation}

	The amplitude is similar to the torus amplitude; first, with a fixed $t = -i\tau$, we have:
	\begin{equation}
		\ave*{
			\prod_i \normorder{e^{ik_i\cdot X_i}}
		}_{\!\!t}
		= iC\, (2\pi)^d\,
			\delta^d\pqty{\textstyle\sum_i k_i}\,
			\exp \Bqty{
				- \sum_{i<j} k_i\cdot k_j\,
					G'(w_i,w_j)
				- \frac{1}{2} \sum_{i} k_i^2
					G'(w_i,w_i)
			}
	\label{eq:amp_generic}
	\end{equation}
	But with a different propagator $G'$, which can be obtained via the method of images; this leads to a doubling of the exponents compared to the torus amplitude:
	\begin{gather}
		G'(w,w')
		= G'_{T^2}(w,w')
			+ G'_{T^2}(w,-\bar{w}'),
	\\
		\ave*{
			\prod_i \normorder{e^{ik_i\cdot X_i}}
		}_{\!\!t}
		= iC\, (2\pi)^d\,
			\delta^d\pqty{\textstyle\sum_i k_i}\,
			\prod_{i < j}
				\abs{W_{ij}(t)}^{
					2\times \alpha'k_i\cdot k_j
				}
	\end{gather}
	Here $W_{ij}(t)$ is the ``corrected'' distance on $T^2$; as $w\to w'$ we have $W_{ij}\sim w_{ij} = w_i - w_j$.

	On the other hand, the vacuum amplitude is given by:
	\begin{equation}
		Z = iV_d \int_0^\infty
			\frac{\dd{t}}{2t}\,
			\pqty{8\pi^2\alpha't}^{-d/2}
			\eta(it)^{-(d-2)}
	\end{equation}
	The $bc$ ghost contributions is included in the $
		\abs{\eta(it)}^2
		= \pqty\big{\eta(it)}^2
	$ factor; note that for $t > 0,\,\eta(it)>0$. Combining this and $
		\ave*{\prod_i \normorder{e^{ik_i\cdot X_i}}}_t
	$, we obtain the final $n$-tachyon amplitude:
	\begin{equation}
		\mcal{A}
		= ig_o^n\, (2\pi)^d\,
			\delta^d\pqty{\textstyle\sum_i k_i}
			\int_0^\infty
				\frac{\dd{t}}{2t}\,
				\pqty{8\pi^2\alpha't}^{-d/2}
				\eta(it)^{-(d-2)}
			\prod_k \int_{\pd M} \dd{w_k}
			\prod_{i<j}
				\abs{W_{ij}(t)}^{
					2\times \alpha'k_i\cdot k_j
				}
	\end{equation}
	Here $\pd M$ is the two ends of the cylinder.

	As is suggested in \arxiv{0812.4408}, it is convenient to introduce the following parametrization for the operator insertions at each boundary:
	\begin{equation}
		w_i = \frac{1 - (-1)^\sigma}{2}\,\pi
			+ 2\pi it\cdot x_i,
	\quad
		0\le x_i\le 1
	\end{equation}
	$\sigma = 0,1$ labels the left and right boundary.

	We want 2 insertions at each boundary, labeled by $
		i = 1,2,\,\sigma = 0
	$, and $
		i = 3,4,\,\sigma = 1
	$; the amplitude can then be reduced to:
	\begin{equation}
	\small
	\begin{gathered}
		\mcal{A}
		= ig_o^n\, (2\pi)^d\,
			\delta^d\pqty{\textstyle\sum_i k_i}
			\prod_k 2\!\int_0^1 \dd{x_k}
			\int_0^\infty
				\frac{\dd{t}}{2t}\,
				\pqty{8\pi^2\alpha't}^{-d/2}
				\eta(it)^{-(d-2)}
				(2\pi t)^n
			\prod_{i<j}
				\abs{W_{ij}(x_{ij},t)}^{
					2 \alpha'k_i\cdot k_j
				},
	\\
		W_{ij}(x_{ij},t)
		= \eta(it)^{-3}\,
			\vartheta_{1,2} \pqty{
				ix_{ij} t \,\big|\, it
			}\,
			\exp \pqty{-\pi x^2_{ij} t}
	\end{gathered}
	\end{equation}
	There is an additional factor of $2$ since $
		\int_{\pd M} \dd{\omega} = 2\int \dd{x}
	$, which includes the contribution after exchange of the two ends $
		12\leftrightarrow 34
	$. 
	Also, $\vartheta_{1,2} = \vartheta_1$ or $\vartheta_2$, depending on whether the vertex operators $i$ and $j$ are on the same boundary or not; this is because:
	\begin{equation}
		\vartheta_1 \pqty{
			ix_{ij} t - \tfrac{1}{2} \,\big|\, it
		}
		= -\vartheta_2 \pqty{
			ix_{ij} t \,\big|\, it
		}
	\end{equation}

	The $\eta(it)^{-3}$ factor in $W_{ij}$ can be further extracted using the on-shell condition $\alpha'k_i^2 = 1$. More specifically, we have:
	\begin{equation}
		\sum_{i<j}
			2 \alpha'k_i\cdot k_j
		= \alpha' \pqty\bigg{\sum_i k_i}^{\!\!2}
			- \alpha' \sum_i k_i^2
		= 0 - n = -n
	\end{equation}
	Therefore, we have:
	\begin{equation}
	\small
	\begin{gathered}
		\mcal{A}
		= ig_o^n\, (2\pi)^d\,
			\delta^d\pqty{\textstyle\sum_i k_i}
			\prod_k \int_0^1 \dd{x_k}
			\int_0^\infty
				\frac{\dd{t}}{t}\,
				\pqty{8\pi^2\alpha't}^{-d/2}
				(2\pi t)^n
				\eta(it)^{\bm{3n}-(d-2)}
			\prod_{i<j}
				\abs{W'_{ij}(x_{ij},t)}^{
					2 \alpha'k_i\cdot k_j
				},
	\\
		W'_{ij}(x_{ij},t)
		= \vartheta_{1,2} \pqty{
				ix_{ij} t \,\big|\, it
			}\,
			\exp \pqty{-\pi x^2_{ij} t}
	\end{gathered}
	\end{equation}
